Statistical Computing (MATH6173) Coursework 2

### 2023-01-07 draft_report.Rmd
Final review of report

For acceptance-rejection sampling (A-R sampling) we need to find a constant $M>0$ such that $\pi(x) \leq Mg(x), \forall x \in \mathbb{R}$. With $\pi(x)$ the target density (the density from which we want to generate a sample of random values) and $g(x)$ the proposal density defined in equations 1 and 2 above respectively. This constant M determines the acceptance probability which is $\frac{1}{M}$ and hence the efficiency of the algorithm. For multiple possible values of $\lambda$ in $g(x)$ the value of $\lambda$ that results in a smaller constant M will have a higher acceptance probability and thus will be our preferred value of $\lambda$ for the algorithm. To find M for each of the proposed $\lambda$ values I split the real domain of $x$ into 3 regions (see plot 1) that I call 1,2 and 3 which correspond to the different expressions of $\pi(x)$ depending on the value of $x$. Then study the relationship between $g(x)$ and $\pi(x)$ within these 3 regions to find $M_{1},M_{2},M_{3}$ which correspond to the smallest constant such that $\pi(x) \leq M_{i}g(x)$ for all possibles values of $x$ in the ith region. Then set $M=max(M_{1},M_{2},M_{3})$ as this is the smallest constant that satisfies $\pi(x) \leq Mg(x)$ for all possible values of $x \in \mathbb{R}$.

@@

## Part b:
To implement A-R sampling using the proposal density with $\lambda=0.5$ and thus $M=3.2e^{0.875}$ to obtain samples from $\pi(x)$ with parameters $s$, $a$ and $b$ I use the following algorithm:

>>>>

For acceptance-rejection sampling (A-R sampling) we need to find a constant $M>0$ such that $\pi(x) \leq Mg(x), \forall x \in \mathbb{R}$. With $\pi(x)$ the target density (the density from which we want to generate a sample of random values) and $g(x)$ the proposal density defined in equations 1 and 2 above respectively. This constant M determines the acceptance probability which is $\frac{1}{M}$ and hence the efficiency of the algorithm. For multiple possible values of $\lambda$ in $g(x)$ the value of $\lambda$ that results in a smaller constant M will have a higher acceptance probability and thus will be our preferred value of $\lambda$ for the algorithm. To find M for each of the proposed $\lambda$ values I split the real domain of $x$ into 3 regions (see plot 1) that I call 1,2 and 3 which correspond to the different forms of the equation of $\pi(x)$ depending on the value of $x$. Then study the relationship between $g(x)$ and $\pi(x)$ within these 3 regions to find $M_{1},M_{2},M_{3}$ which correspond to the smallest constant such that $\pi(x) \leq M_{i}g(x)$ for all possibles values of $x$ in the ith region. Then set $M=max(M_{1},M_{2},M_{3})$ as this is the smallest constant that satisfies $\pi(x) \leq Mg(x)$ for all possible values of $x \in \mathbb{R}$.

@@

## Part b:
To implement A-R sampling using the proposal density with $\lambda=0.5$ and thus $M=3.2e^{0.875}$ to obtain samples from $\pi(x)$ with parameters $s$, $a$ and $b$ I used the following algorithm:
